\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-11-07 related-work.tex
related work on EP

Pumpkin Pi~\cite{ringer2021pumpkin} is a Coq plug-in that helps
repair proofs broken by changes in type definitions.
Its decompiler from proof terms to proof scripts prioritizes suggesting
useful tactics over soundness.
While Pumpkin Pi focuses on refactoring existing proofs in response to
changed definitions,
the focus of our solution is preempting refactoring altogether by
writing code that has built-in hooks for future extensions.

\bigskip

@@

\textbf{Solution to The Expression Problem}
% Have no idea how to write this :(

>>>>

Pumpkin Pi~\cite{ringer2021pumpkin} is a Coq plug-in that helps
repair proofs broken by changes in type definitions.
Its decompiler from proof terms to proof scripts prioritizes suggesting
useful tactics over soundness.
While Pumpkin Pi focuses on refactoring existing proofs in response to
changed definitions,
our solution can be viewed as an effort to preempt refactoring by
allowing the programmer to write code that has built-in hooks for
future extensions.

\noindentparagraph{Solutions to the expression problem} abound.
Our approach is the first that applies family polymorphism~\cite{ernst2001family},
an idea found in the context of OO programming,
to the context of mechanized proofs.
Families in \Lang are second-class, in that they are not considered
terms by themselves.
Families as modeled in \TT (namely linkages) are first-class and thus more flexible.
The distinction corresponds to class-based vs.\ object-base family
polymorphism as summarized before~\cite{cdnw07-tribe}.

\citet{bac2006} address the expression problem in a functional language,
introducing a language mechanism that allows pattern-matching cases to
be added retroactively in accordance with extensions to variant types.
Our \lsti{FRecursion} and \lsti{FInduction} commands achieve a similar
functionality, with families bestowing additional organizational power.

@@
